\documentclass[margin,line]{res}

\topmargin=-0.8in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\textheight=12in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.1in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.1in}}}{\end{list}}


\begin{document}
\small
\name{\Large Ayb\"{u}ke \"{O}zdemir Kaya\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Info}
\begin{tabular}{@{}p{2in}p{3.8in}}
aybuke.147@gmail.com & {\hfill{\it}  +90 (554) 343-2144} \\
\end{tabular}
\begin{tabular}{@{}p{2in}p{3.8in}}
www.aybukeozdemir.blogspot.com medium.com/@aybuke\_ozdemir& {\hfill{\it}  github.com/aybuke} \\
\end{tabular}

\vspace*{-.3cm}
\section{\sc E\u{g}\.{I}t\.{I}m}

{\bf \c{C}anakkale 18 Mart \"{U}niversity}, \c{C}anakkale, Turkey  \hfill {\bf 2011 - 2016} \\

\vspace*{-.7cm}
{\em Bachelor's Degree, Computer Engineering} \hfill {\ } \\
\vspace*{-.09in}
\vspace*{-.3cm}


\vspace*{-.3cm}
\section{\sc Experiances}

{\bf VNGRS, Devops Engineer}, Istanbul, Turkey \hfill {\bf May 2018 - Now}\\

\vspace{-.7cm}
{\em Devops Team }
\vspace*{+.05in}
\begin{list2}
\item I found the opportunity to work on AWS, Azure and Google Cloud. Other than cloud services, I used technologies such as docker, kubernetes, helm, terraform, ansible, jenkins, circleci.
\end{list2}

{\bf EBrandValue, Devops Engineer}, Istanbul, Turkey \hfill {\bf November 2016 - May 2018}\\

\vspace{-.7cm}
{\em Devops Team}
\vspace*{+.05in}
\begin{list2}
\item \c I have experienced writing Ansible, Terraform and Dockerfile scripts; using Marathon/Mesos for container orchestration. Same time I worked actively in Django/Python(Backend) enhancements and oncall rotation.

\end{list2}

{\bf Metglobal, Intern}, Istanbul, Turkey \hfill {\bf June 2014}\\

\vspace{-.7cm}
{\em System Management Team }
\vspace*{+.05in}
\begin{list2}
\item Puppet Policy-Base Autosigning i\c{c}in bir sorgulama beti\u{g}i yazd{\i}m. 

(https://github.com/aybuke/policy-based-for-PUPPET).
\end{list2}

{\bf Gamegos, Intern}, Istanbul, Turkey \hfill {\bf August 2013}\\

\vspace{-.7cm}
{\em System Management Team}
\vspace*{+.05in}
\begin{list2}
\item I wrote Python library for Haproxy config file and Rest API for this library. 

(Repos: https://github.com/aybuke/hapra, https://github.com/aybuke/python-haproxy-tools).
\end{list2}

\section{\sc Projects and Contributions}
\begin{list2}
\item {\bf LibreOffice: The patches I have prepared for Libreoffice are as follows:.}

https://gerrit.libreoffice.org/\#/q/aybuke+status:merged
\item {\bf Outreachy 2014-2016: The patches I have prepared for Linux Kernel are as follows:.}

https://patchwork.kernel.org/project/opw-kernel/list/?submitter=90241\&archive=both
\item {\bf I'm one of the contributor Mozilla Balrog Project:} Balrog using as app update service by Mozilla Developers.(AUS)

https://github.com/mozilla/balrog-ui/
\item {\bf I'm one of the contributor LibreOffice Crash Project:} Crash using as crash report for Libreoffice servers.

https://github.com/mmohrhard/crash/
\item {\bf My Pebble Smartwatch App: Magic Button:}

https://github.com/pebble-tr/Magic-Button
\item {\bf I'm one of the contributor Pebble Watchface Textwatch-tr:}

https://github.com/pebble-tr/PebbleTextWatch-tr
\item {\bf I'm member of LibreOffice and Mozilla transtation team:}

https://support.mozilla.org/tr/kb/locales/tr

https://wiki.documentfoundation.org/Language/\c{C}evirmenler/tr
\end{list2}
\vspace{-.3cm}

\section{\sc Presentations and Certifications}
\begin{list2}
\item LPIC1 ve OpenSuse Certification (id: LPI000278784)
\item Ham Certification (TA3IOQ)
\item Pythonsaati 46 Virtualization at the Application Layer (2018)
\item Pythonsaati 36 Infrastructure as Code (2018)
\item Free Software ve Linux Days (2016)  LibreOffice Development and Dissemination Meeting 
\item Academic Informatics Conference - Ayd{\i}n \"{U}niversity (2016) LibreOffice Development Workshop (4 days)
\item Academic Informatics Conference - Ayd{\i}n \"{U}niversity (2016) Free Software Opportunity for Women
\item Bal{\i}kesir University (2016) Free Software and Free Society Seminar
\item Devfest Istanbul (2015) Contributing LibreOffice and Our Experiences
\item INET-TR (2015) Women and Informatics Seminar 
\item DevFest Student Eski\c{s}ehir (2014) Contributing Linux Kernel and Our Experiences
\item Mu\u{g}la 2. Free Software Workshop (2014) Contributing Linux Kernel and Our Experiences
\item Free Web Tecnological Days (2014) Administrate Puppet Certifications
\item Academic Informatics Conference - Mersin University (2014) Free Software Opportunity for University Students
\item Free Web Tecnological Days (2013) What is Haproxy and Hapra?
\end{list2}
\vspace{-.3cm}

\section{\sc Abilities}
\begin{list2}
\item Diller: Turkish, English (B2)
\item Programming Languages: Python, C/C++ {\em little bit Perl, Ruby and Go}.
\item Tools: Vim, Git, Gerrit, Mercurial, SSH, Screen, Terraform, Docker, Kubernetes, Helm, Ansible, Jenkins, CircleCi
\item Frameworks: Django, Tornado, Flask, Chalice
\end{list2}

\vspace{-.3cm}
\section{\sc Hobbies}
\begin{list2}
\item Contributing for free software project.
\item Reading novel and comics. Watching series and films.
\item Playing drum and midi keyboard.
\item Drawing something.
\end{list2}

\end{resume}
\end{document}
